### 2019-03-18 papers.tex
Pull in paper 12, directly from the future
Pull in Jenny's paper

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addpaper
	{93\% of paint splatters are valid Perl programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{\vspace{0.15in} {\scriptsize The authors assure us the materials will be available ``soon'' from: \url{http://famicol.in/sigbovik}} \raisebox{0in}{\includegraphics[height=0.75in]{participation}}}

\addtrack
	{}{Back to the future}
\addpaper
	{Need more RAM? Just invent time travel!}
	{Robert Andrews, Mitchell Jones, Patrick Lin, and the UIUC Theory CS Group}
	{Keywords: complexity, Turing machine, time travel}
	{SIGBOVIK_2019_paper_23}
	{0cm}
	{}
\addpaper
	{On CLI-based Renderers: In which we investigate the utility of rendering teapots in a command line}
	{Michael Sandler}
	{Keywords: teapot, render, speed and performance, command-line interface, CLI, graphics}
	{SIGBOVIK_2019_paper_40}
	{0cm}
	{}
\addpaper
	{SpaceF}
	{Oscar Hernandez and The Space Invaders}
	{Keywords: space, invasion, moonshot, government, \#yeswecandotherightthingandnotgotospace, extraterrestrial intelligence, National Rifle Association, cheese, George Mallary}
	{SIGBOVIK_2019_paper_30}
	{0cm}
	{}

>>>>

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addpaper
	{93\% of paint splatters are valid Perl programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{\vspace{0.15in} {\scriptsize The authors assure us the materials will be available ``soon'' from: \url{http://famicol.in/sigbovik}} \raisebox{0in}{\includegraphics[height=0.75in]{participation}}}
\addpaper
	{A survey and projection of SIGBOVIK trends}
	{Jenny H. Lin}
	{Keywords: SIGBOVIK, self referential, ``Figures'', join the committee}
	{SIGBOVIK_2019_paper_chair}
	{0cm}
	{}

\addtrack
	{}{Back to the future}
\addpaper
	{Need more RAM? Just invent time travel!}
	{Robert Andrews, Mitchell Jones, Patrick Lin, and the UIUC Theory CS Group}
	{Keywords: complexity, Turing machine, time travel}
	{SIGBOVIK_2019_paper_23}
	{0cm}
	{}
\addpaper
	{WICCAN: (deep) learning directly from the future}
	{Amanda Coston and Alan Mishler}
	{Keywords: deep learning, data-free, dark arts}
	{SIGBOVIK_2019_paper_12}
	{0cm}
	{}
\addpaper
	{On CLI-based Renderers: In which we investigate the utility of rendering teapots in a command line}
	{Michael Sandler}
	{Keywords: teapot, render, speed and performance, command-line interface, CLI, graphics}
	{SIGBOVIK_2019_paper_40}
	{0cm}
	{}
\addpaper
	{SpaceF}
	{Oscar Hernandez and The Space Invaders}
	{Keywords: space, invasion, moonshot, government, \#yeswecandotherightthingandnotgotospace, extraterrestrial intelligence, National Rifle Association, cheese, George Mallary}
	{SIGBOVIK_2019_paper_30}
	{0cm}
	{}
